---
title: "Additional LP Problems"
author: "ms"
date: "9/30/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Transportation by Trucks

### Problem formulation

Variable Definition

* qi continuous: tonnes of raw material to purchase in quarter i
* si continuous: tonnes in stock at the end of quarter i, and s0 as the initial stock
* ti integer: small trucks to contract in quarter i
* ui integer: large trucks to contract in quarter i

Objective Function

Min: 20q1 + 25q2 + 30q3 + 40q4 + 8s1 + 8s2 + 8s3 + 8s4 + 700t1 + 700t2 + 700t3 + 700t4 + 1400u1 + 1400u2 + 1400u3 + 1400 u4;

Demand constraints

```
sini: s0 = 100;
dem1: s0 + q1 - s1 = 1000;
dem2: s1 + q2 - s2 = 1200;
dem3: s2 + q3 - s3 = 1500;
dem4: s3 + q4 - s4 = 1800;
sfin: s4 = 100;

Truck capacity constraints

cap1: q1 - 500t1 - 1200u1 <= 0;
cap2: q2 - 500t2 - 1200u2 <= 0;
cap3: q3 - 500t3 - 1200u3 <= 0;
cap4: q4 - 500t4 - 1200u4 <= 0;

Declaration

int t1, t2, t3, t4, u1, u2, u3, u4;
```

#### Read file

```{r}
library(lpSolveAPI)
y <- read.lp("TransportationbyTrucks.lp")
y
```

### Solve the problem
```{r}
solve(y)
get.objective(y)
```

### Print the solution
```{r}
t1 <- get.variables(y)
s0t1 <- t1[17]
t1 <- t1[-17]
t1m <- matrix(t1,ncol = 4,nrow = 4)
t1mt <- t(t1m)
t1mt <- cbind(c(NA,s0t1,NA,NA),t1mt)
rownames(t1mt) <- c("Purchased","Stock","Small Trucks","Large Trucks")
colnames(t1mt) <- c("0","1","2","3","4")
knitr::kable(t1mt,caption="Transportation by Trucks")
```

******************

## Hiring and Firing Example

### Problem Formulation

```
// Objective function
min: 5h1 + 5h2 + 5h3 + 5h4 + 5h5 + 5h6 + 10f1 + 10f2 + 10f3 + 10f4 + 10f5 + 10f6 + 8s1 + 8s2 + 8s3 + 8s4 + 8s5 + 8s6;

// Constraints

sini: s0 = 20;
sm1: s0 + h1 - f1 - s1 = 0; 
sm2: s1 + h2 - f2 - s2 = 0;
sm3: s2 + h3 - f3 - s3 = 0; 
sm4: s3 + h4 - f4 - s4 = 0;
sm5: s4 + h5 - f5 - s5 = 0;
sm6: s5 + h6 - f6 - s6 = 0;

// Now, bi = 1 if we hire somebody
h1 - 1000 b1 <= 0;
h2 - 1000 b2 <= 0;
h3 - 1000 b3 <= 0;
h4 - 1000 b4 <= 0;
h5 - 1000 b5 <= 0;
h6 - 1000 b6 <= 0;

// We cannot fire anybody in a month when we hired in the previous month
// f(i+1) <= M (1-bi)
// f(i+1) + M b1 <= M

f2 + 1000 b1 <= 1000;
f3 + 1000 b2 <= 1000;
f4 + 1000 b3 <= 1000;
f5 + 1000 b4 <= 1000;
f6 + 1000 b5 <= 1000;

// Minimum staff required

s1 >= 30;
s2 >= 60;
s3 >= 55;
s4 >= 40;
s5 >= 45;
s6 >= 50;

// Declare binary variables

bin b1, b2, b3, b4,  b5, b6;

```

### Read File

```{r}
library(lpSolveAPI)
x <- read.lp("HiringFiring.lp")
x
```

### Now, solve the problem
```{r}
solve(x)
get.objective(x)
```

### Now, print the solution

```{r}
v1 <- get.variables(x)
s0 <- v1[19]
v1 <- v1[-19]
<<<<<<< HEAD
v1
=======
>>>>>>> c59631b3ff730f26b02ad95664b60a7ab74fd84a
tt <- c(NA,NA,s0,NA)
v <- matrix(v1,ncol=4,nrow=6)
v <- t(v)
v <- cbind(tt,v)
rownames(v) <- c("Hired","Fired","Staff","Hired")
colnames(v) <- c("Period 0","Period 1","Period 2","Period 3","Period 4","Period 5","Period 6")
knitr::kable(v,caption = "Optimal Model for Staff Planning")
```
