---
title: "Goal Programming"
author: "MS"
date: "October 7, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal Programming
This file contains solutions to the problems discussed in class
```{r}
library(lpSolveAPI)
gp1 <- read.lp("gp1.lp")
gp1
write.lp(gp1,"test.lp")
```
### Solve
```{r}
solve
(gp1)
get.objective(gp1)
```
### Solution
```{r}
get.variables(gp1)
get.constraints(gp1)
```

#### Remarks
Note that Y2+ is 8.333, so this solution adds nearly 20% more to the workforce. Consequently, management has concluded that a very high priority should be placed on avoiding an increase in the workforce. Furthermore, management has learned that raising more than $55 million for capital investment for the new products would be extremely difficult, so a very high priority also should be placed on avoiding capital investment above this level.

## Sequential Approache - Preemptive Programming
In our first goals, we minimize the hiring and capital expenses, with only those constraints.
```{r}
gp2 <- read.lp("gp2.lp")
gp2
```
### Solve
```{r}
solve(gp2)
get.objective(gp2)
```
#### Remarks
Note that the solution is zero. So, these goals have now been met, and we can incorporate them as part of the constraints, where y2+ and y3+ are zero.

### Revised GP Model

Here is the revised model

```{r}
gp3 <- read.lp("gp3.lp")
gp3
```
#### Solve
```{r}
solve(gp3)
get.objective(gp3)
```
#### Solution
```{r}
get.variables(gp3)
```

