---
title: "Group Assignment"
output: html_notebook
---

This is the logic I followed for my toy (example) problem, which is to assign a total of six students to one of three groups.

Variables

Xij = 1, if person i belongs to group j; 0 otherwise

Constraints

1. A person can belong to no more than one group
2. A group requires two people
3. Now, I say that each group should have a minimum of 2 in programming skills. I used the first 6 people from the survey in assigning the coefficients. The first six people have skill levels 1, 1, 1, 3, 3, 1. The question is why 2? It turns out that using a higher number gives me an infeasible solution.

Objective

This is maximization problem where I try to maximize the programming skills for each group.

Here is the program

```{r}
library(lpSolveAPI)
x <-read.lp("group_ass.lp")
x
solve(x)
get.objective(x)
```

Remember that the solution is presented in the order in which variables appear in the formulation
```{r}
get.variables(x)
```

The solution indicates that X31 and X51 belong to Group 1; X22 and X42 belong to Group 2, and X13 and X63 belong to Group 3. In other words, Students 3 and 5 in Group 1, 2 and 4 in Group 2, and 1 and 6 in Group 3.
```{r}
get.constraints(x)

```



