---
title: "Group Assignment"
output: html_notebook
---

This is the logic I followed:

1. We have 21 students who need to be assigned into 7 groups of 3
2. We have data on the following characteristics of the students:
  a) Programming skills
  b) Comfort with public speaking
  c) Years of experience
  d) Background (I have ignored this in the formulation below)

Variables

Xij = 1, if person i belongs to group j; 0 otherwise

Constraints

1. A person can belong to no more than one group
2. A group requires three people
3. For each of the characteristics, each group must meet a minimum value. I initially determined the minimum value by looking at the data, and I then kept adjusting it until I saw parity.

Objective

This is maximization problem where I try to maximize the programming skills for each group. We can also use the other characteristics, or all of them.

Here is the program

```{r}
library(lpSolveAPI)
x <-read.lp("ga.lp")
x
```

Now, to solve it. As this is a pure Integer programming problem, the solution can take time
```{r}
system.time(solve(x))
get.objective(x)
```

Remember that the solution is presented in the order in which variables appear in the formulation
```{r}
Assignment <- get.variables(x)
Assignment
```

How good is the solution
```{r}
get.constraints(x)
```

Let us now map the student names to the solution
First read the names
```{r}
snames <- as.matrix(read.csv("./snames.txt"))
```

Now, we are going to join the student names to the Assignment solution. But, these two columns are of different length, so we will repeat the snames to get at the right number of rows as Assignment. We use a new package called mefa.

We should probably put some check to ensure that the row lengths are correct.
```{r}
library(mefa)
snames <- rep(snames,length(Assignment)/length(snames))
```

We now join the two columns
```{r}
if (length(Assignment) == length(snames)) {
  Solution <- cbind(Assignment,snames)
  Solution <- subset(Solution, Assignment == "1") 
  group = 1
  repeat {
    ul <- group * 3
    ll <- ul -2
    print(c("Group",group,Solution[c(ll:ul),2]))
    group <- group + 1
    if (group > 7) {
      break
    }
  }
}
```
