---
title: "SA"
author: "ms"
date: "10/22/2018"
output: html_document
---

Ref: Generalized Simulated Annealing for Global Optimization: The GenSA Package
An Application to Non-Convex Optimization in Finance and Physics
by Yang Xiang, Sylvain Gubian, Brian Suomela and Julia Hoeng

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Load Libraries

```{r}
library(GenSA)
library(ggplot2)
library(GA)
```

#### Define Function and Solve

```{r}
# The following function requires two inputs
# Limits are (-3,-3) to (3, 3)
 fun = function(x,y) { (sin(10*x)*cos(10*y)+2)/sqrt(x^4+y^4+1) } 
 obj = function(z) { -fun(z[1],z[2])}
 lower <- c(-3,-3)
upper <- c(3,3)
par <- c(2,2)
```

```{r}
# Plot the function
x=seq(-3,3,length=50) # tick marks on x axis
y=seq(-3,3,length=50) # tick marks on y axis; defines grid for... 
z=outer(x,y,fun) # matrix for plotting -- z vals / height of surface
 persp3D(x, y, z, phi = 0, theta = 45,
  xlab = "X", ylab = "Y",
  main = "Surface elevation data",
  color.palette = bl2gr.colors
)
filled.contour(x, y, z, color.palette = bl2gr.colors)
```


```{r}
out <- GenSA(par=par,lower=lower,upper=upper,fn=obj)
out[c("value","par","counts")]
filled.contour(x, y, z, color.palette = bl2gr.colors, 
      plot.axes = { axis(1);
                    axis(2); points(out$par[1],out$par[2],
                                    cex=2,col="red",lwd=2)}
)
```


#### Define another function

```{r}
 nfun = function(x) {
   (12*x^5-975*x^4+28000*x^3-345000*x^2+1800000*x)
 }
ll = c(0)
ul = c(31)

# Plot the function
# Note, plotting as a maximization function
p <- ggplot(data=data.frame(x=0),aes(x=x))
p + stat_function(fun=nfun) + xlim(0,31)
```

#### Solve using GenSA

Note that GenSA only solves minimization problems by default
```{r}
nfun1 = function(x) { -nfun(x)}
ll = c(0)
ul = c(31)
par = 2
out1 <- GenSA(par=par,lower=ll,upper=ul,fn=nfun1)
out1[c("value","par","counts")]
curve(nfun, from = 0, to = 31, n = 1000)
points(out1$par[1],-out1$value, col = 2, pch = 19)
```

#### Portfolio Optimization

Reference: https://cran.r-project.org/web/packages/PortfolioAnalytics/vignettes/portfolio_vignette.pdf

Mean-risk models were developed in the 1950s for portfolio selection problems. Value-at-Risk (VaR) and Conditional Value-at-Risk (CVaR) are the most popular measures of downside risk. Mullen et al. (2011) and Ardia et al. (2011) used DEoptim to find the portfolio weights for which the portfolio has the lowest CVaR and each investment can contribute at most 22.5% to total portfolio CVaR risk. For details, please refer to Mullen et al. (2011); Ardia et al. (2011). The code for objective function in portfolio optimization are from Ardia et al. (2011) (https://journal.r-project.org/archive/2011/RJ-2011-005/RJ-2011-005.pdf)  

```{r}
library("quantmod")
tickers <- c("GE", "IBM", "GOOG", "AMZN", "AAPL")
getSymbols(tickers, from = "2004-12-01", to = "2018-10-27")
P <- NULL
for(ticker in tickers) {
 tmp <- Cl(to.monthly(eval(parse(text = ticker))))
 #print(tmp)
 P <- cbind(P, tmp)
}
colnames(P) <- tickers
R <- diff(log(P))
R <- R[-1,]
mu <- colMeans(R)
sigma <- cov(R)
library("PerformanceAnalytics")
pContribCVaR <- ES(weights = rep(0.2, 5), method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)$pct_contrib_ES
obj <- function(w) {
 fn.call <<- fn.call + 1
 if (sum(w) == 0) { w <- w + 1e-2 }
 w <- w / sum(w)
 CVaR <- ES(weights = w, method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)
 tmp1 <- CVaR$ES
 tmp2 <- max(CVaR$pct_contrib_ES - 0.225, 0)
 out <- tmp1 + 1e3 * tmp2
 return(out)
}
```
```{r}
set.seed(43298)
fn.call <<- 0
out.GenSA <- GenSA(fn = obj, lower = rep(0, 5), upper = rep(1, 5), control = list(smooth = FALSE, max.call = 3000))
fn.call.GenSA <- fn.call
out.GenSA$value
out.GenSA$counts
cat("GenSA call functions", fn.call.GenSA, "times.\n")
wstar.GenSA <- out.GenSA$par
wstar.GenSA <- wstar.GenSA / sum(wstar.GenSA)
rbind(tickers, round(100 * wstar.GenSA, 2))
100 * (sum(wstar.GenSA * mu) - mean(mu))
```
